---
title: "Assignment 3"
author: "Krishan"
date: "2024-09-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Dataset


```{r}
data<-read.csv("/Users/krishanbhalsod/Desktop/online_gaming_behavior_dataset.csv")
```
## Clean Data.

```{r}
data$InGamePurchases<-NULL
```

## Creating a Histogram

This is a histogram that shows the range of play time hours for every game. The distribution does appear to be normal. It doesn't skew in either direction, so if I did want to analyze this data further, a t-test would suffice.

```{r}
hist(data$PlayTimeHours,main="Range of Play Time Hours",xlab="Hours",ylab="Frequency")
```

## Creating a Scatter Plot

I will be creating a scatter plot to check if there's a correlation between the age and the number of sessions per week. I created a linear regression line and of course there's no correlation. Age and the number of sessions have no correlation.

```{r}
library(ggplot2)
ggplot(data,aes(x=Age, y=SessionsPerWeek))+
  geom_point(color = "black")+
  geom_smooth(method = "lm", se = FALSE, color = "blue")+
  labs(title = "Age vs Sessions Per Week",x = "Age",y="Sessions Per Week")
```
## Statistical Calculation

For my statistical calculation, I will create a hypothesis saying that games with a high engagement level will have high play time hours. First I will perform basic statistical calculations such as the average session time and the average play time hours. Then I will perform a t-test

```{r}
mean(data$SessionsPerWeek)
mean(data$PlayTimeHours)
```

## T-Test

```{r}
high_engagement<-subset(data, EngagementLevel=="High")
not_high_engagement <-subset(data,EngagementLevel!="High")
t_test <- t.test(high_engagement$PlayTimeHours, not_high_engagement$PlayTimeHours)
t_test
```
## Conclusion

With a p-value of 0.4437, it's safe to say that we do not have enough evidence to support the alternative hypothesis where high engagement level means high play time hours.
